Trans-dimensional Bayesian Inference and Nested Sampling

### 2014-08-06 Documents/Talk/content.tex
Bayes 101

\begin{frame}[t]{Bayesian Inference 101}
Probabilities describe degrees of plausibility

Uncertain quantities described by probability distributions

@@

>>>>

\begin{frame}[t]{Bayesian Inference 101: I}
Bayesian Inference is a unified framework for solving inference problems.
We need the following ingredients:

\begin{itemize}
\item A ``hypothesis space'' describing the set of possible answers to our
question (``parameter space'' in fitting is the same concept).
\item A ``prior distribution'' $\pi\left(\theta\right)$ describing how plausible
each of the possible solutions is, not taking into account the data.
\end{itemize}

@@

\begin{frame}[t]{Bayesian Inference 101: II}

The data helps us by changing our prior distribution into the ``posterior''
distribution, given by
\begin{eqnarray}
\frac{\pi(\theta)\mathcal{L}(\theta)}{\mathcal{Z}}
\end{eqnarray}
\end{frame}
